Title

### 2024-06-30 paper/main.tex
Updates

Understanding cause-and-effect relationships between variables is a fundamental
goal in many scientific questions as it reveals the underlying mechanisms of
the observed phenomena and informs effective interventions or policy decisions.
\emph{Causal Discovery} methods aim to uncover the underlying causal structure
among random variables from a given observational dataset. The problem of
causal discovery has been explored in both the Directed Acyclic Graphs (DAGs)
and Structural Equation Models (SEMs) literatures, each with different
approaches. In the DAG literature, the focus has been on developing automated
algorithms that can learn the causal structure from observational datasets. In
contrast, the SEM literature focuses on tools that help researchers manually
construct or modify models.

@@

In the DAG literature, many automated algorithms have been developed for causal
discovery such as constraint based methods like PC \citep{Spirtes2001} and FCI
\citep{Spirtes2000}, score-based methods like Hill-Climb Search, Greedy
Equivalence Search \citep{Chickering2002}, and optimization based methods.
However, the adaption of these algorithms in applied fields remain limited
\citep{Tennant2020}. Researchers in applied fields typically prefer to
construct DAGs manually based on their domain knowledge. We hypothesize that
this preference towards manual DAG construction stems from the following
challenges in applying causal discovery algorithms:

\begin{enumerate}
	\item \textbf{Trustworthiness: } Although most algorithms have
		asymptotic theory proving them to be consistent, their finite
		sample properties are not well understood. Moreover, depending
		on the selected hyperparameters of the algorithms, the output
		can vary very significantly. In real-world settings with finite
		samples, these algorithms can make obvious mistakes, for
		example, the constraint-based algorithms are biased towards
		sparse graphs \citep{Malinsky2024}. Consequently, researchers
		often have rely on post-hoc modifications based on model
		testing methods and their domain knowledge.
	\item \textbf{Outputs Markov Equivalence Class (MEC):} Multiple causal
		structures can be faithful to a given observational dataset.
		Thus, using only observational data, these algorithms can only
		recover the MECs that can contain unoriented edges. However,
		most methods for downstream tasks, such as identification or
		causal effect estimation, assume knowledge of a fully oriented
		DAG. As a result, researchers have to rely on their expertise
		to orient these edges or make further assumptions to make use
		of pairwise orientation techniques.
	% \item \textbf{Algorithm and hyperparameter selection:} Each algorithm
	% 	has the same goal but they can learn very different models
	% 	depending on the choice of algorithm and their hyperparameters.
	% 	For example, the choice of the conditional independence (CI)
	% 	test being used for constraint-based method depends on the
	% 	dataset, similarly for the scoring method for score-based
	% 	methods. With no obvious way to test the impact/performance of
	% 	these choices on a given dataset, it becomes quite hard to
	% 	chose the optimal algorithm for a given dataset.
\end{enumerate}

As a result of these challenges, doesn't matter if the researcher is manually
constructing the DAG or using an algorithm, they need to do some manual
modifications to the model before being able to use them for analysis. One of
the common ways to guide this modification is to use Conditional Independence
(CI) based model testing \cite{Ankan2021}. As DAGs imply CI statements that can
be tested in the given data, and then model can be modified based on the
p-values of these test. Figure~\ref{fig:ci_testing} shows an example of testing
using CIs. This approach has two main drawbacks:
\begin{enumerate}
	\item CIs are implied by missing edges only, and hence we can not test
		whether an incorrect edge is present in the model.
	\item For larger graphs, the number of CI tests can be very large, for
		example, the alarm network with $ 37 $ nodes has $ 287 $
		implied CIs. It can be difficult to look at all these tests for
		violations.
\end{enumerate}

@@

On the other hand, in Structural Equation Models (SEMs) literature, more
emphasis has been placed on helping researchers manually construct models while
integrating their expertise. Researchers typically develop an initial model
based on domain knowledge and use various tools to guide modifications to
improve the fit of their model to data while it still making theoretical sense.
This model construction process is known as \emph{Specification Search}. A
common method for specification search is \emph{modification indices}, which
identify potential changes to the model structure that improve the model fit
and ranks them using the most improvement to the model fit. This ranking allows
the researchers to focus first on the suggestions that can improve the model
the most and while integrating their expertise to choose the most optimal
modifications.

\todo[inline]{Show a figure of how the output looks like for modification indices}
\todo[inline]{Other methods: Modification indices and Lagrange Multiplier tests to
selectively add edges And using Wald test or z statistics (also known as
critical ratios) for removing edges.}

Inspired by this ranking approach, in this paper we present a way to rank the CI 
testing using a measure of association. This can be interpreted as the edge

Our proposed approach uses a measure of association to find correlated variables
in the data that are not explained by the current model. Using the measure, we 
can rank the edge that can lead to the highest explanation of the observed 
correlation. Based on this information, the user can select a potential edge
and based on their expert knowledge decide the direction of the edge.

% We present a similar procedure for modifying DAGs based on expert knowledge and
% measure of association. We first use the measure of association to test whether
% the association observed in the data is explained by the model structure. We
% can not directly use the local CI tests to make modifications because that
% would give way too many independencies and we have no way to rank them. Based
% on this testing, we suggest adding edges by ranking them by the most
% unexplained association between variables. The researcher can then use expert
% knowledge to decide the direction of the edge between the variables.

Our main contributions in this papers are as follows:
\begin{enumerate}
	\item We present a measure of (conditional) association for mixed data
		based on canonical correlations. This measure of association
		generalizes the widely used partial correlation to mixed data
		setting.
	\item Using this association measure, we present a procedure to suggest
		modifications (i.e., new edges, and deleting edges) to a given
		model such that the model can better explain the observed
		associations in the data. 
	\item Lastly, we present a web-browser based tool to allow researchers
		to apply this method to their own datasets.
\end{enumerate}

@@

			\draw[->]  (age) to[bend right=20] (ed);
			\draw[->]  (sex) to (ed);
			\draw[->]  (age) to (hrpw);
			\draw[->]  (ed) to (hrpw);
			\draw[->]  (sex) to (hrpw);
			\draw[->]  (ed) to (income);
			\draw[->]  (hrpw) to (income);
			\draw[->]  (occ) to[out=300, in=0, looseness=1.4] (income.east);
			\draw[->]  (sex) to (income);
			\draw[->]  (ed) to[out=90, in=150, looseness=1.3] (occ);
			\draw[->]  (sex) to (occ);	
		\end{scope}
		\begin{scope}[xshift=-3cm]
			\draw[thick, ->, double, cyan] (2.5,0) -- (3,0);
			\node[rectangle, align=center, inner sep=1pt] at (5, 0) {
				\begin{minipage}{.2\textwidth}
					\begin{equation*}
						\begin{split}
							\textnormal{Age} &\ci \textnormal{Incm} \rvert \textnormal{Edct, Hrpw, Sex} \\
							\textnormal{Age} &\ci \textnormal{Occp} \rvert \textnormal{Edct, Sex} \\
							\textnormal{Age} &\ci \textnormal{Sex} \\
							\textnormal{Hrpw} &\ci \textnormal{Occp} \rvert \textnormal{Edct, Sex} \\
						\end{split}
					\end{equation*}
				\end{minipage}
				};
		\end{scope}
		\end{tikzpicture}
		\caption{\todo[inline]{Finish figure to show an example of model testing}}
		\label{fig:ci_testing}
\end{figure}
\begin{figure}
	\caption{\todo[inline]{Placeholder for figure showing an example of modification indices}}
\end{figure}

@@

\todo[inline]{Add more notation as they come}

\subsection{Measures of (Conditional) Association}
As our DAG construction procedure relies on a measure of conditional
association between variables, in this section we list out some of the already
known measures for specific data types. These measure of associations are
typically the effect size of various conditional indepdnence tests but they
don't need to be. However, there are no generalized measure of association for
mixed data, that we propose in the next section. This is by no means an
exhaustive list, rather just to give an idea of what can be done.

@@

\todo[inline]{Is it even possible}

@@

In this section, we define a novel partial measure of association for mixed
data by extending the idea of partial correlation to mixed data. We do this by
combining a mixed-data residualization method with a multivariate measure of
association. Given $ n $ samples $ D = (x, y, \bm{z}) $ of variables $ X $, $ Y $,
and $ \bm{Z} $, we are interested in computing an estimate of the conditional
association $ \rho(X, Y; \bm{Z}) $ between $ X $ and $ Y $ conditioned on $
\bm{Z} $. As the residualization approach requires atleast one conditional
variable to be present, if $ \bm{Z} = \emptyset $, we use a constant value for
$ Z $. Firstly, we compute the residuals for $ X $ and $ Y $ using the $ \bm{Z}
$ as the predictor variables. We use the mixed data residualization approach
from \citet{Ankan2023}. The residual computation depends on the type of 
variable:

\begin{enumerate}
	\item \textbf{$ X $ is continuous:} We start by training a regression
		model, $ E_X: x \sim \bm{z} $. Next we take the predictions
		from this model $ \hat{x} = E_X(\bm{z}) $ and lastly the
		residuals are computed as the difference between the true and
		the predicted values.
		$$ R_{x_i} = x_i - \hat{x}_i $$
	\item \textbf{$ X $ is ordinal:} We start by training a probability
		estimator, $ p_X: x \sim \bm{z} $, and take probability
		predictions from it $ \hat{p}_X: \hat{p}_X(\bm{Z}) $. Then we
		compute the residuals as follows:
		$$ R_{x_i} = \hat{p}(\hat{x}_i > x_i) - \hat{p}(\hat{x}_i < x_i) $$
	\item \textbf{$ X $ is categorical:} We again start by training a
		probability estimator $ p_X: X \sim \bm{Z} $, and take the
		probability estimates from it $ \hat{p}_X: p_Z(\bm{Z}) $. Next,
		we one-hot encode the categorical variable and then compute the
		residuals as follows: 
		$$ R_X = x_i - \hat{p}(\bm{z}_i) $$
\end{enumerate}

@@

Here, users have the option to choose the estimators based on the properties of
their data. Non-parametric ensemble estimators such as Random Forest and
XGBoost can work well on a large variety of data and any data type. For linear
datasets users can also choose variants of linear regression depending on the
type of data. After the above steps are repeated for both $ X $ and $ Y $, we
end up with two residual matrices: $ R_X $ and $ R_Y $. The type of the
variable determines the shape for these matrices, i.e., if the variable is
continuous we get a residual matrix of shape $ ( n \times 1 ) $ and if the
variable is categorical we have a residual matrix of shape $ ( n \times (k-1))
$ (where one of the dummy encoded variables is dropped to avoid
multicollinearity)

We now have two continuous valued residual matrices and we need a measure to
quantify the association between these residuals. In multivariate statistics,
canonical correlation based measures have been used for measuring association
between two sets of variables. We can treat the residuals as sets of variables
in case of categorical variable and use canonical corrleations to quantify the
association between them.
\todo[inline]{Justify the argument}

\begin{definition}
	Given two sets of random variables $ \bm{U} = (U_1, U_2, \cdots, U_p) $
	and $ \bm{V} = (V_1, V_2, \cdots, V_q) $, canonical correlation between
	them, $\rho(\bm{U}, \bm{V}) $ is defined as:

	\begin{equation}
		\rho(\bm{U}, \bm{V}) = \sup_{a, b} \frac{a^T \Sigma_{\bm{U}\bm{V}} b}{\sqrt{a^T \Sigma_{\bm{U}\bm{U}} a} \sqrt{b^T \Sigma_{\bm{V}\bm{V}} b}}
	\end{equation}

@@

We use Pillai's Trace for our purpose for two main reasons: 1) It uses all the
canoncial correlation values, 2) Its interpretation is similar to correlation
coefficient, i.e., $ 0 $ signifies no association and $ 1 $ signifies perfect
linear relationship.

\todo[inline]{Add the formula for our case here}

@@

\begin{enumerate}
	\item Bounded between $ 0 $ and $ 1 $.
	\item Independent of sample size.
	\item Invariant to the one-hot encoding scheme used fr categorical variables.
	\item Reduces to partial correlations when both variables are continuous.
	\item In case of discrete variables, connected to Cramer\'s V, a well
		known effect size measure for discrete variables.
		\todo[inline]{Show the connection}
\end{enumerate}

@@

@@

@@

\subsection{Results}
\begin{figure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics{../code/plots/shd_ribbon.pdf}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics{../code/plots/sid_ribbon.pdf}
		\caption{}
	\end{subfigure}
	\caption{Comparison of PC and Hill-Climb Search algorithms against
		manually drawn DAGs using the assistance method. As PC and
		Hill-Climb Search return the Markov Equivalence Class (MEC), we
		use the best and worst scoring orientation of the MEC to get
		the range of values. The human drawn values are done for
		multiple accuracy values of the oracle.}
\end{figure}

@@

@@

\bibliography{references}
\end{document}

>>>>

Understanding cause-and-effect relationships between variables is a fundamental
goal in many scientific questions as it reveals the underlying mechanisms of
observed phenomena and informs effective interventions or policy decisions.
\emph{Causal Discovery} methods aim to uncover the underlying causal structure
among random variables from a given observational dataset. The problem of
causal discovery has been explored in both the Directed Acyclic Graphs (DAGs)
and Structural Equation Models (SEMs) literatures, each adopting different
approaches. In the DAG literature, the focus has primarily been on developing
automated algorithms that can learn the causal structure from observational
datasets. In contrast, the SEM literature has focused more towards developing
tools that assist researchers in manually constructing or modifying models.

@@

As a result of these efforts, numerous approaches to automated algorithms for
causal discovery have been proposed in the DAG literature, including
constraint-based method like the PC algorithm \citep{Spirtes2001} and Fast
Causal Inference (FCI) \citep{Spirtes2000}), score-based methods like
Hill-Climb Search and Greedy Equivalence Search (GES) \citep{Chickering2002},
and continuous optimization-based methods like NO TEARS \citep{Zheng2018} and
DAGMA \citep{Bello2022}. However, the adaption of these algorithms in applied
fields remain limited, and researchers typically prefer to construct DAGs
manually based on their domain expertise \citep{Tennant2020, Petersen2021}.
Even when using automated algorithms, users often rely on manual post hoc
modifications to the model learned by the algorithm because they:

\begin{enumerate}
	\item \textbf{Make Obvious Mistakes:} Although most algorithms are
		theoretically consistent asymptotically, their finite sample
		properties are not well understood. Moreover, depending on the
		selected hyperparameters, their output can vary significantly.
		These issues combined with no good method to test the
		performance of these algorithms on a given dataset, in
		real-world settings with finite samples, these algorithms can
		make obvious mistakes. Consequently, users have to rely on
		posthoc modifications to the model based on their domain
		expertise.
	\item \textbf{Outputs Markov Equivalence Class (MEC):} Multiple
		DAGs can be faithful to a given observational dataset. Thus,
		using only observational data, algorithms can only recover the
		MECs that can contain a combination of directed and undirected
		edges. However, most methods for downstream tasks, such as
		identification or causal effect estimation, assume knowledge of
		a fully oriented DAG. As a result, users have to manually
		orient these edges before using them for analysis.
\end{enumerate}

Due to these challenges, whether constructing the model manually or using an
algorithm, users must rely on their domain expertise to construct or modify the
model. Hence, it is crucial to have tools to guide this modification process.
One of the ways to guide this modification is to use Conditional Independence
(CI) based model testing \cite{Ankan2021}. As DAGs imply CI statements that can
be tested in the given data using statistical CI tests, we can verify whether
the implied CIs are consistent in the data or not. If some of implied CIs are
not valid in the given dataset, we can modify the model accordingly.
Figure~\ref{fig:ci_testing} shows an example of model testing using CIs.
However, this CI testing approach has a few drawbacks. Firstly, as CIs are
implied only by missing edges in the model, we can not test whether an
incorrect edge is already present in the model. Secondly, the number of implied
CIs can be quite large. For example, in the moderately sized alarm network with 
$ 37 $ node, there are $287$ implied CIs. If we rely only on the p-values of the
CI tests, it can be difficult to figure which test to focus on.

@@

On the other hand, in Structural Equation Models (SEMs) literature, more
emphasis has been placed on developing tools to help researchers manually
construct models while integrating their domain expertise. Researchers
typically develop an initial model based on domain knowledge and use various
tools to guide modifications to improve the fit of their model to data. This
model construction process is known as \emph{Specification Search}. A common
method for specification search is using \emph{modification indices}, which
identify potential changes to the model structure that improve the model fit.
These potential changes are then ranked by the ones that improve the fit the
most. This ranking allows the researchers to focus first on the suggestions
that can improve the model the most and while integrating their expertise to
choose the most optimal modifications.

Inspired by this ranking approach in modification indices, in this paper we
develop a method to rank the CI tests using a conditional measure of
association. Our proposed approach uses the measure of association to find
correlated variables in the data that are not explained by the current model.
Using the measure, we can then rank the pair of variables between which adding
an edge would improve the explanation the most. Based on this information, the
user can select a potential pair of variables and based on their expert
knowledge decide the direction of the edge. Our main contributions in this
paper are as follows:
\begin{enumerate}
	\item We present a measure of (conditional) association for mixed data
		based on canonical correlations. This measure of association
		generalizes the widely used partial correlation to mixed data
		setting.
	\item Using this association measure, we present a procedure to suggest
		modifications (i.e., new edges, and deleting edges) to a given
		model such that the model can better explain the observed
		associations in the data. 
	\item Lastly, we present a web-browser based tool to allow researchers
		to apply this method to their own datasets.
\end{enumerate}

@@

			\draw[->]  (age) to[bend right=20] (ed);
			\draw[->]  (sex) to (ed);
			\draw[->]  (age) to (hrpw);
			\draw[->]  (ed) to (hrpw);
			\draw[->]  (sex) to (hrpw);
			\draw[->]  (ed) to (income);
			\draw[->]  (hrpw) to (income);
			\draw[->]  (occ) to[out=300, in=0, looseness=1.4] (income.east);
			\draw[->]  (sex) to (income);
			\draw[->]  (ed) to[out=90, in=150, looseness=1.3] (occ);
			\draw[->]  (sex) to (occ);	
		\end{scope}
		\begin{scope}[xshift=-3cm]
			\draw[thick, ->, double, cyan] (2.5,0) -- (3,0);
			\node[rectangle, align=center, inner sep=1pt] at (5, 0) {
				\begin{minipage}{.2\textwidth}
					\begin{equation*}
						\begin{split}
							\textnormal{Age} &\ci \textnormal{Incm} \rvert \textnormal{Edct, Hrpw, Sex} \\
							\textnormal{Age} &\ci \textnormal{Occp} \rvert \textnormal{Edct, Sex} \\
							\textnormal{Age} &\ci \textnormal{Sex} \\
							\textnormal{Hrpw} &\ci \textnormal{Occp} \rvert \textnormal{Edct, Sex} \\
						\end{split}
					\end{equation*}
				\end{minipage}
				};
		\end{scope}
		\end{tikzpicture}
		\caption{\todo[inline]{Finish figure to show an example of model testing}}
		\label{fig:ci_testing}
\end{figure}
\begin{figure}
	\caption{\todo[inline]{Figure showing an example of modification indices}}
\end{figure}

@@

\subsection{Measures of (Conditional) Association}
\todo[inline]{Complete this section}
As our DAG construction procedure relies on a measure of conditional
association between variables, in this section we list out some of the already
known measures for specific data types. These measure of associations are
typically the effect size of various conditional indepdnence tests but they
don't need to be. However, there are no generalized measure of association for
mixed data, that we propose in the next section. This is by no means an
exhaustive list, rather just to give an idea of what can be done.

@@

@@

In this section, we develop a novel partial measure of association for mixed
data by extending the idea of partial correlation to mixed data. We do this by
combining a mixed-data residualization method with a multivariate measure of
association. Given $ n $ samples $ D = (x, y, \bm{z}) $ of variables $ X $, $ Y
$, and $ \bm{Z} $, we are interested in computing an estimate of the
conditional association $ \rho(X, Y; \bm{Z}) $ between $ X $ and $ Y $
conditioned on $ \bm{Z} $. As the residualization approach requires atleast one
conditional variable to be present, if $ \bm{Z} = \emptyset $, we use a
constant value for $ Z $. Similar to partial correlation, we first compute the
residuals for $ X $ and $ Y $ using $ \bm{Z} $ as the predictor variables. We
use the mixed data residualization approach from \citet{Ankan2023}. Depending
on the type of dependent variable, the residuals are defined as follows:

\begin{enumerate}
	\item \textbf{Continuous:} We train a regression
		model, $ E_X: x \sim \bm{z} $. The residuals are then defined
		as the difference between the true and the predicted value using
		$ E_X $.
		$$ R_{x_i} = x_i - E_X(\bm{z}_i) $$
	\item \textbf{Ordinal:} We start by training a probability
		estimator, $ p_X: x \sim \bm{z} $, and take probability
		predictions from it $ \hat{p}_X: \hat{p}_X(\bm{Z}) $. Then we
		compute the residuals as follows:
		$$ R_{x_i} = \hat{p}(\hat{x}_i > x_i) - \hat{p}(\hat{x}_i < x_i) $$
	\item \textbf{Categorical:} We again start by training a
		probability estimator $ p_X: X \sim \bm{Z} $, and take the
		probability estimates from it $ \hat{p}_X: p_Z(\bm{Z}) $. Next,
		we one-hot encode the categorical variable and then compute the
		residuals as follows: 
		$$ R_X = x_i - \hat{p}(\bm{z}_i) $$
\end{enumerate}

@@

Here, users have the option to choose the estimators based on the properties of
their data. Non-parametric ensemble estimators such as Random Forest and
XGBoost can work on any combination of data types while performing reasonably
well. For linear datasets users can also choose variants of linear regression
depending on the type of data. After the above steps are repeated for both $ X
$ and $ Y $, we end up with two residual matrices: $ R_X $ and $ R_Y $. The
type of the variable determines the shape for these matrices, i.e., if the
variable is continuous we get a residual matrix of shape $ ( n \times 1 ) $ and
if the variable is categorical we have a residual matrix of shape $ ( n \times
(k-1)) $ (where one of the dummy encoded variables is dropped to avoid
multicollinearity)

We now have two continuous valued residual matrices and the second step now is
to quantify the association between these residuals. In multivariate
statistics, canonical correlation based measures have been used for measuring
association between two sets of variables. We can treat the residuals as sets
of variables in case of categorical variable and use canonical correlations to
quantify the association between them.
\todo[inline]{Justify the argument}

\begin{definition}
	Given two sets of random variables $ \bm{U} = (U_1, U_2, \cdots, U_p) $
	and $ \bm{V} = (V_1, V_2, \cdots, V_q) $, canonical correlation between
	them, $\phi(\bm{U}, \bm{V}) $ is defined as:

	\begin{equation}
		\phi(\bm{U}, \bm{V}) = \sup_{a, b} \frac{a^T \Sigma_{\bm{U}\bm{V}} b}{\sqrt{a^T \Sigma_{\bm{U}\bm{U}} a} \sqrt{b^T \Sigma_{\bm{V}\bm{V}} b}}
	\end{equation}

@@

We use Pillai's Trace for our purpose for two main reasons: 1) It uses all the
canoncial correlation values, 2) Its interpretation is similar to correlation
coefficient, i.e., $ 0 $ signifies no association and $ 1 $ signifies perfect
linear relationship. This gives us the following partial measure of association:

$$ \rho(X, Y; \bm{Z}) = \sum_{i=1}^{min(\rvert R_X \rvert, \rvert R_Y \rvert)} (\phi_i(R_X, R_Y))^2 $$

@@

\begin{enumerate}
	\item Bounded between $ 0 $ and $ 1 $.
	\item Independent of sample size.
	\item Invariant to the one-hot encoding scheme used fr categorical variables.
	\item Reduces to partial correlations when both variables are continuous.
	\item In case of discrete variables, connected to Cramer\'s V, a well
		known effect size measure for discrete variables.
\end{enumerate}
\todo[inline]{Expand on these points}

@@

\todo[inline]{Add screenshots here}

@@

\begin{figure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics{../code/plots/shd_ribbon.pdf}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics{../code/plots/sid_ribbon.pdf}
		\caption{}
	\end{subfigure}
	\caption{Comparison of PC and Hill-Climb Search algorithms against
		manually drawn DAGs using the assistance method. As PC and
		Hill-Climb Search return the Markov Equivalence Class (MEC), we
		use the best and worst scoring orientation of the MEC to get
		the range of values. The human drawn values are done for
	multiple accuracy values of the oracle. \todo[inline]{Replace Hill-Climb with GES}}
\end{figure}

@@

\subsection{Results}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[scale=0.3]{../code/plots/llm_adult.png}
	\caption{\todo[inline]{Change figure to have consistent style}}
\end{figure}

@@

\newpage
\bibliography{references}
\end{document}
